Comparing software variability across and within fMRI analysis packages

### 2022-04-12 paper/paper.tex
Update small changes

\maketitle
\begin{abstract}
  Variability has been broadly observed in functional MRI analyses as a
  result of software differences both between and within analytic tools.
  However, the relationship between within-tool and between-tool software
  variabilities for a given analysis is unclear. Within-tool variability has multiple origins
  including variations in algorithms, parametrizations, and
  low-level software dependencies. We focus on the effects resulting from software dependencies --- 
  in particular due to operating system and other infrastructural updates --- as they often remain unnoticed 
  while algorithms and parametrizations are more controllable.
 We extended
  a previous comparison of fMRI analysis software libraries (namely FSL,
  AFNI, and SPM) and related the observed differences to within-tool
  software variability simulated using Monte-Carlo arithmetic. In group
  analyses, we found that
  between-tool software variability was consistently larger than within-tool software
  variability. In subject analyses, within-tool software variability
  approached between-tool software variability in some regions for some subjects.
  Interestingly, within- and between-tool software variabilities appeared moderately
  correlated ($r > 0.5$ across voxels) in all tested conditions. 
  % Finally, we found that
  % within-tool software variability had effects of similar magnitude to between-tool
  % software variability when simulated from numerical perturbations introduced at the virtual
  % precision of 17 bits --- a high but plausible level of uncertainty for
  % scientific computing libraries. \tristan{Revise from latest results}
  % %  \gk{What does this mean? They only have
  % precision of 17, or they use data that is 17 bits?}
  %  \yohan{agree with Greg, it is unclear and a strong assertion!}
  %  \camille{It is not entirely clear to me how this relates to the previous
  %  conclusions that BT variability was consistently larger than machine
  %  error} \tristan{Better?}
  Our findings motivate the continued investigation of within-tool
  software variability in neuroimaging, and position it as a possible proxy
  for studying some of the arbitrary between-tool software variations for
  subject-level analyses.
\end{abstract}

@@

For both group- and subject-level analyses, between- and within-tool
software variabilities were found to be moderately correlated. Even though
both types of variability are different in nature, this result suggests
that in some cases they may have a common cause that might be related to
the conditioning of fMRI analysis in a specific dataset. Along these lines,
in some regions, instabilities of similar magnitude may be triggered by
small numerical perturbations, model variations, or implementation
differences. For instance, high-motion datasets may trigger between- and
within-tool instabilities similarly.

>>>>

\maketitle
\begin{abstract}
  Variability has been broadly observed in functional MRI analyses as a
  result of software differences both between and within analytic tools.
  However, the relationship between within-tool and between-tool software
  variabilities for a given analysis is unclear. Within-tool variability has multiple origins
  including variations in algorithms, parametrizations, and
  low-level software dependencies. We focus on the effects resulting from software dependencies --- 
  in particular due to operating system and other infrastructural updates --- as they often remain unnoticed 
  while algorithms and parametrizations are more controllable.
 We extended
  a previous comparison of fMRI analysis software libraries (namely FSL,
  AFNI, and SPM) and related the observed differences to within-tool
  software variability simulated using Monte-Carlo arithmetic. In group
  analyses, we found that
  between-tool software variability was consistently larger than within-tool software
  variability. In subject analyses, within-tool software variability
  approached between-tool software variability in some regions for some subjects.
  Interestingly, the brain masking instability was triggered by both within- and between-tool
  software variabilities.
  % Finally, we found that
  % within-tool software variability had effects of similar magnitude to between-tool
  % software variability when simulated from numerical perturbations introduced at the virtual
  % precision of 17 bits --- a high but plausible level of uncertainty for
  % scientific computing libraries. \tristan{Revise from latest results}
  % %  \gk{What does this mean? They only have
  % precision of 17, or they use data that is 17 bits?}
  %  \yohan{agree with Greg, it is unclear and a strong assertion!}
  %  \camille{It is not entirely clear to me how this relates to the previous
  %  conclusions that BT variability was consistently larger than machine
  %  error} \tristan{Better?}
  Our findings motivate the continued investigation of within-tool
  software variability in neuroimaging, and position it as a possible proxy
  for studying some of the arbitrary between-tool software variations for
  subject-level analyses.
\end{abstract}

@@

For both group- and subject-level analyses, between- and within-tool
software variabilities similarly trigger the brain masking instability.
Even though both types of variability are different in nature, this result suggests
that in some cases they may have a common cause that might be related to
the conditioning of fMRI analysis in a specific dataset. 
% Along these lines,
% in some regions, instabilities of similar magnitude may be triggered by
% small numerical perturbations, model variations, or implementation
% differences. For instance, high-motion datasets may trigger between- and
% within-tool instabilities similarly.
